Plant Trait Imputation

### 2024-05-03 code/L1/L1_P4_TropicalAndes_plant_imputetraits.Rmd
Update L1_P4_TropicalAndes_plant_imputetraits.Rmd
add code to retrive trait data from BIEN & GIFT using family and genus

# retrieve list of species without family & genus information
species_no_family <- na_species_df %>%
  filter(is.na(family) | family == "") %>%
  select(species) %>%
  pull()
species_no_genus <- na_species_df %>%
  filter(is.na(genus) | genus == "") %>%
  select(species) %>%
  pull()
# check if all the species in no_family & no_genus lists are the same
identical(species_no_family, species_no_genus)
```
Use taxize for species with no family and genus info
```{r}
library(taxize)

@@

##Retrive trait records for species using BIEN & GIFT
```{r}

>>>>

# retrieve list of species without family & genus information
species_no_family <- na_species_df %>%
  filter(is.na(family) | family == "") %>%
  select(species) %>%
  pull()
species_no_genus <- na_species_df %>%
  filter(is.na(genus) | genus == "") %>%
  select(species) %>%
  pull()
# check if all the species in no_family & no_genus lists are the same
identical(species_no_family, species_no_genus)
```
Use taxize for species with no family and genus info
```{r, results='hide',message=FALSE, warning=FALSE}
library(taxize)

@@

##Retrive trait records for species using BIEN & GIFT
```{r}
# Dispersal Syndrome
Dispersal.Syndrome_families_BIEN <- BIEN_trait_traitbyfamily(family = Dispersal.Syndrome_families, trait = "dispersal syndrome")
Dispersal.Syndrome_genus_BIEN <- BIEN_trait_traitbygenus(genus = Dispersal.Syndrome_genus, trait)

Dispersal.Syndrome_families_GIFT <- GIFT_traits_tax(trait_IDs = "3.3.1")
Dispersal.Syndrome_families_GIFT <- Dispersal.Syndrome_families_GIFT[Dispersal.Syndrome_families_GIFT$family %in% Dispersal.Syndrome_families, ]
```

```{r}
# Fruit Length
Fruit.Length_families_BIEN <- BIEN_trait_traitbyfamily(family = Fruit.Length_families, trait = c("maximum fruit length", "minimum fruit length"))
Fruit.Length_genus_BIEN <- BIEN_trait_traitbygenus(genus = Fruit.Length_genus, trait = c("maximum fruit length", "minimum fruit length"))

Fruit.Length_families_GIFT <- GIFT_traits_tax(trait_IDs = "3.13.3")
Fruit.Length_families_GIFT <- Fruit.Length_families_GIFT[Fruit.Length_families_GIFT$family %in% Fruit.Length_families, ]
```

```{r}
# Plant Height
Plant.Height_families_BIEN <- BIEN_trait_traitbyfamily(family = Plant.Height_families, trait = "whole plant height")
Plant.Height_genus_BIEN <- BIEN_trait_traitbygenus(genus = Plant.Height_genus, trait = "whole plant height")

Plant.Height_families_GIFT <- GIFT_traits_tax(trait_IDs = "1.6.3")
Plant.Height_families_GIFT <- Plant.Height_families_GIFT[Plant.Height_families_GIFT$family %in% Plant.Height_families, ]
```

```{r}
# Fruit Type
Fruit.Type_families_BIEN <- BIEN_trait_traitbyfamily(family = Fruit.Type_families, trait = "fruit type")
Fruit.Type_genus_BIEN <- BIEN_trait_traitbygenus(genus = Fruit.Type_genus, trait = "fruit type")

Fruit.Type_families_GIFT <- GIFT_traits_tax(trait_IDs = "3.16.1")
Fruit.Type_families_GIFT <- Fruit.Type_families_GIFT[Fruit.Type_families_GIFT$family %in% Fruit.Type_families, ]
```

```{r}
# Growth Form
Growth.Form_families_BIEN <- BIEN_trait_traitbyfamily(family = Growth.Form_families, trait = "whole plant growth form")
Growth.Form_genus_BIEN <- BIEN_trait_traitbygenus(genus = Growth.Form_genus, trait = "whole plant growth form")

Growth.Form_families_GIFT <- GIFT_traits_tax(trait_IDs = "1.2.1")
Growth.Form_families_GIFT <- Growth.Form_families_GIFT[Growth.Form_families_GIFT$family %in% Growth.Form_families, ]
```
